Measuring Software Ticket Quality using Quantitative Data Analysis

### 2018-04-23 paper/paper.tex
Finish analysis section

Sentiment analysis is a technique of employing Machine Learning algorithms in order to infer a sentiment 
score from textual information. These algorithms need to be trained on very large data sets in order to 
produce valuable results. Moreover, we would have also needed an already annotated data set, which means 
a number of strings where we compute the score by hand given a mathematical formula we define. Even though 
there are open source libraries that can help creating and employing the algorithms, such as TensorFlow, 
we would still have needed tickets where we defined what do we mean by positive/negative tickets, as well as
manually computing the scores for a large range of them. Therefore, we ended using a third party API - Google 
Cloud Platform Natural Language Processing, considered the best such service at the moment. This API returns 
a score between -1 (most negative) and +1 (most positive) for any text encoded in the HTTP request.

After we concatenated summaries, descriptions and all the comments for every ticket, we started sending our 
requests to Google and we plotted the data shown in Figure \ref{sentiment}. A correlational analysis revealed a 
weak negative relationship with $r = -0.114$, $p < 0.01$. Therefore, we obtained statistically significant 
results implying that as the sentiment decreases (i.e. becomes more negative), the Time-To-Close increases, thus 
decreasing the quality of a ticket.

We can see in the Figure that neutral scores (i.e. between -0.42 and 0.42) show rather neutral results, which 
was expectable: this most probably implies that the discussions and descriptions for these tickets revolved 
completely around the ticket and nothing else.

However, as the sentiment decreases, we can clearly observe that the sentiment scores increase significantly. 
This might signify that once the discussion becomes \"heated\", the developers might lose interest in solving 
the task anymore. Also, rude language might be a driver for increased Times-To-Close because when developers are 
answering questions from the reporters (or vice versa), the other person might become rude or unpolite, which can 
make them feel unwelcomed and start to lose interest in helping the project anymore.

@@

A solution for pushing towards this ideal scenario would be expensive for the company, but the most efficient - have a 
sentiment analysis tool running in the background as the user is typing in any text box. If they reach a certain low 
treshold and it is believed that they are becoming rude or unpolite, there could be a warning/pop-up on the screen advising 
them to not do that as it wouldn't help any party, but rather try to be polite, engaging and friendly. One other solution
is a much more cost-effective one, but less efficient - the issue tracking system administrators could include a section 
in the code of conduct for the project stating that promoting a positive environment will help everyone. This way, people 
revolving around the project might be more inclined to be friendly.

>>>>

Sentiment analysis is a technique of employing Machine Learning algorithms in order to infer a sentiment 
score from textual information. These algorithms need to be trained on very large data sets in order to 
produce valuable results. Moreover, we would have also needed an already annotated data set, which means 
a number of strings where we compute the score by hand given a mathematical formula we define. Even though 
there are open source libraries that can help with creating and employing the algorithms, such as TensorFlow, 
we would still have needed tickets where we defined what is meant by positive/negative tickets, as well as
manually computing the scores for a large range of them. Therefore, we ended using a third party API - Google 
Cloud Platform Natural Language Processing, considered the best such service at the moment. This API returns 
a score between -1 (most negative) and +1 (most positive) for any text encoded in the HTTP request.

After we concatenated summaries, descriptions and all the comments for every ticket, we sent our 
requests to Google and we plotted the data shown in Figure \ref{sentiment}. A correlational analysis revealed a 
weak negative relationship with $r = -0.114$, $p < 0.01$. Therefore, we obtained statistically significant 
results implying that as the sentiment decreases (i.e. becomes more negative), the Time-To-Close increases, thus 
decreasing the quality of a ticket.

We can see in Figure \ref{sentiment} that neutral scores (i.e. between -0.42 and 0.42) correspond to rather 
average \emph{Times-To-Close}, as was expected.

However, as the sentiment decreases, we can clearly observe that the \emph{Time-To-Close} increases significantly. 
This might signify that once the discussion becomes "heated", the developers might lose interest in solving 
the task anymore. Also, rude language might be a driver for increased \emph{Times-To-Close}: the engineer might become 
rude or impolite, which can make the interlocutor feel unwelcome and start to lose interest in helping the project anymore.

@@

A solution for pushing towards this ideal scenario would be expensive for the company, but the most efficient - have a 
sentiment analysis tool running in the background as the user is typing in any text box. If they reach a certain low 
threshold and it is believed that they are becoming rude or unpolite, there could be a warning/pop-up on the screen advising 
them against submitting the comment and encouraging them to be polite, engaging and friendly. One other solution
is a much more cost-effective one, but less efficient - the issue tracking system administrators could include a section 
in the code of conduct for the project stating that promoting a positive environment will help everyone. This way, people 
revolving around the project might be more inclined to be friendly.
